RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-02 review/response.tex

\begin{reviewer}
	The paper studies the achievable rates for both primary transmission and backscatter information, assuming a Gaussian distribution for primary transmission and K tags (with M loads each) and a single source-destination primary link; the authors assume full CSI knowledge and formulate a mutual information maximization problem, with probability distribution of loads per tag as a function to be optimized (in conjunction with beamforming weights for the multi-antenna transmitter and energy thresholds for the energy-based detector for the backscatter information). The problem is non-convex and challenging, and the authors revert to a series of approximations to relax it and offer a solution. The methodology is interesting in two ways: a) the authors do not employ SIC, but instead focus first on the tags' (weak) information signal, since its knowledge renders the detection of the primary information as a simple coherent detection problem, and b) borrow techniques from the discrete memoryless MAC/discrete memoryless thresholding channel literature, in order to calculate the average rate of the backscattered information.

	The authors balance rate of primary transmission with rate of backscattered tags in a unified, user-controlled way and offer comparison results with prior art in the field (e.g., bistatic backscatter, where no primary link information is present, ambient backscatter, symbiotic (cooperative) ambient backscatter and RIS). Of particular importance is the fact that the authors have modeled both small-scale (through Rice) and large-scale (through distance) fading link parameters, typically omitted in many comm theory papers, even though backscattered links are operating in the presence of the much stronger primary link.

	Overall, the methodology and overall presentation is rigorous and deserves further attention. Having said that, the following remarks are offered:

	\point CSI estimation impact: the notion of full and perfect CSI knowledge is a very strong assumption; the authors do point at footnote 4, page 8 (single column version) to CSI estimation literature. However, CSI estimation for ambient backscatter employs several assumptions and simplifications and it is not perfect or ideal. The authors should perhaps study in terms of simulations the impact of imperfect CSI and necessary degrees of freedom (for channel estimation) on the achieved rates, carefully taking into account the tag(s) small SNR as well as the primary link much stronger SNR.
	\reply {We agree with the reviewer that the assumption of perfect CSI is very strong. Fast and accurate acquisition of cascaded CSI can be challenging especially when the backscatter SNR is weak and/or the number of nodes is large. To investigate the impact of CSI estimation error on the system performance, we have applied the proposed algorithms to an imperfect CSI model, where the cascaded channel of node $k$ is estimated as
		\begin{equation}
			\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
		\end{equation}
		$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
	}

	\point Modeling assumptions: the overall model is based on Gaussian codebooks for the primary link and lack of structural mode for backscattering; the latter is assumed absorbed by the channel parameters (Section II.A), while the tags are assumed with a demodulator/receiver of the primary information; it is also assumed that both full CSI and reflection efficiency parameters $\{\alpha_k\}, k \in \{1, 2, \ldots, K\}$ are known for all tags, while each tag is equipped with a receiver/demodulator (for the primary information). The reviewer believes that the structural mode cannot be absorbed by the channel parameters, since it offers a DC term, while there is no practical way to estimate separately the cascaded channel from the reflection efficiency; moreover, receivers in tags either increase the complexity or reduce the tag's sensitivity, especially when envelope detectors are used (as in Fig. 3). Moreover, the assumption for perfect symbol-level synchronization between tags and source, or the integer ratio between tags and source symbol duration is also very strong. Some discussion on the above is necessary, while some thoughts on non-Gaussian codebooks and how the methodology could be extended is perhaps important.
	\reply {Your valuable comments on scatter modeling and codebook design are very much appreciated. When the transmitted waveform is a continuous carrier wave (CW) that carries no information, the structure mode component is also a CW. After downconversion, its contribution is indeed modelled as a DC offset \cite{Boyer2014}. However, when the transmitted waveform is a modulated signal, the structure mode component is proportional to the modulated signal, and its contribution can thus be absorbed in the environment multipath \cite{Thomas2012,Liang2020}. When estimating the cascaded CSI, the reflection efficiency $\{\alpha_k\}$ can be set to some pre-determined values, such that the cascaded channels can be separated from the reflection efficiency. We agree with the reviewer that adding integrated receivers will increase the complexity and reduce the sensitivity of the nodes. The aim is to coordinate the nodes with the active source and to acquire the optimized input distributions, instead of decoding the primary information dedicated for the user. Thus, those receivers can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity. Besides, the assumption of perfect symbol-level synchronization and integer spreading ratio are made to simplify the achievable rate analysis, and they have been widely adopted in relevant literatures \cite{Liang2020,Ding2020,Long2020a,Guo2019b,Han2021,Zhang2022}. If they are not satisfied, some penalty can be introduced to the achievable rate and it is left for future work. We have incorporated the above discussions in the revised manuscript.}

	\point Independent distributions across tags: (10) assumes independence among distributions of tag loads across tags; IV.D.1 talks about joint nodes encoding; pls clarify. In addition, some more discussion is needed at IV.C and Fig. 9; for $\rho=1$, i.e., primary transmission maximum prioritization, Fig. 9 shows that only one load (out of 4) should be used. The reviewer was puzzled by this. Perhaps, values of the loads used in the simulations and respective reflection coefficients should be explicitly offered, in conjunction with more discussion regarding the wireless channel impact. When the channel changes, one would expect the distribution of the tags' loads to be sensitive on channel statistics.
	\reply {We apologize for the confusion caused by poor writing. The achievable rate analysis and the algorithms are provided for the most general case where all nodes encode independently. When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly. This formulates an augmented backscatter source and becomes a special case of above. Regarding the observation in Fig. 9, please note that one state corresponds to one equivalent load (and one reflection coefficient). In this case, there is exactly one reflection coefficient (corresponds to state 3) that maximizes the primary SNR, and it should be used with probability 1 to maximize the primary rate. Instead of explicitly designing the value of load impedance, we assume that they have been designed to fulfill the reflection coefficient codebook. The node input distribution (not the reflection coefficient codebook) is indeed adaptive to CSI, as mentioned in Section III.A. We have clarified the above points in the revised manuscript.}

	\point All simulation results and respective optimization solutions are offered with relatively small number of K and M; some discussion on ways to extend the methodology for larger networks and loads should be helpful.
	\reply {Thank you for the suggestion. The main limitations for massive RIScatter are the energy detection and the dynamic programming algorithm. For $K$ nodes each with $M$ states, there are a total of $L = M^K$ energy decision regions to design. The candidate threshold set $\mathcal{T}$ should be even finer, which results in a very fast growth of the computational complexity ($\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$ for SMAWK and $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$ for bisection). To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising. We have added this to the conclusion part of the revised manuscript.}

### 2023-08-02 main.tex
:speech_balloon: Add comments

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

@@

\begin{section}{RIScatter}
	\begin{subsection}{Principles}
		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
		It is usually modelled as a DC offset \cite{Boyer2014} or part of environment multipath \cite{Thomas2012}.
		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
		Specifically,
		\begin{itemize}
			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
			The reflection coefficient is used merely an information codeword \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio and $c_m$ is the constellation point.
			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
			The reflection coefficient is used merely a passive beamforming codeword \cite{Wu2018}
			\begin{equation}
				\Gamma_m = \alpha_m \exp(j \theta_m),
				\label{eq:passive_beamforming}
			\end{equation}
			where $\theta_m$ is the phase shift.\footnote{It is commonly assumed $\alpha_m \ll 1$ in \gls{bc} and $\alpha_m=1$ in \gls{ris}.}
		\end{itemize}

@@

		RIScatter nodes can be implemented, for example, by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, recovers the reflection pattern, and coherently decodes the primary link.
		The detail will be covered in Section~\ref{se:system_model}.
	\end{subsection}

	\begin{subsection}{System Model}
		\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{riscatter_network.pdf_tex}
			}
			\caption{A single-user multi-node RIScatter network.}
			\label{fg:riscatter_network}
		\end{figure}
		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
		All nodes have $M$ available reflection states.
		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (no inter-symbol interference).} enhanced by RIScatter nodes.
		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.

		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
		As a sequence of double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
			\end{align}
		\end{subequations}
		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
			\label{eq:receive_signal}
		\end{equation}
		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power budget, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.

		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
		The backscatter symbol $x_k$ (resp. symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp. value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp. $p(x_{m_{\mathcal{K}}})$).
		\begin{remark}
			Dispersed RIScatter nodes encode independently such that
			\begin{equation}
				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
				\label{eq:equivalent_distribution}
			\end{equation}
			When the nodes are co-located, they can jointly encode by designing $p(x_{m_{\mathcal{K}}})$ directly.
		\end{remark}

>>>>

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cw}{CW}{Continuous Waveform}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

@@

\begin{section}{RIScatter}
	\begin{subsection}{Principles}
		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a DC offset in the baseband signal when the impinging signal is a \gls{cw} \cite{Boyer2014}.
		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
		Specifically,
		\begin{itemize}
			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
			The reflection coefficient is used merely an information codeword \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio and $c_m$ is the constellation point.
			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
			The reflection coefficient is used merely a passive beamforming codeword \cite{Wu2018}
			\begin{equation}
				\Gamma_m = \alpha_m \exp(j \theta_m),
				\label{eq:passive_beamforming}
			\end{equation}
			where $\theta_m$ is the phase shift.\footnote{It is commonly assumed $\alpha_m \ll 1$ in \gls{bc} and $\alpha_m=1$ in \gls{ris}.}
		\end{itemize}

@@

		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user. The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, recovers the reflection pattern, and coherently decodes the primary link.
		The detail will be covered in Section~\ref{se:system_model}.
	\end{subsection}

	\begin{subsection}{System Model}
		\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{riscatter_network.pdf_tex}
			}
			\caption{A single-user multi-node RIScatter network.}
			\label{fg:riscatter_network}
		\end{figure}
		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
		All nodes have $M$ available reflection states.
		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.

		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the coded backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
		As a sequence of double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
			\end{align}
		\end{subequations}
		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
			\label{eq:receive_signal}
		\end{equation}
		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power budget, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
